---
title: "Exemplo de apresentação"
author: "Thiago Moreira da Silva"
date: "11 de outubro de 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Gráficos interativos 

```{r pressure}
library(networkD3)
data(MisLinks, MisNodes)
forceNetwork(Links = MisLinks, Nodes = MisNodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.4)
```



## Slide novo

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(gapminder)
library(tidyverse)
library(ggthemes)
library(plotly)

gapminder <- data.frame(gapminder)

g1 <- gapminder %>% 
  filter(country %in% c("Angola", "Brazil", "Argentina",
                        "Cuba", "Canada")) %>% 
  ggplot(aes(year, lifeExp, color = country)) + 
  geom_line() + theme_fivethirtyeight() + 
  scale_y_continuous(limits = c(10,90)) + 
  geom_point() +  theme(legend.position="none")
  
ggplotly(g1)
```


